Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2020-12-03 manuscript/draft_rsfmri.Rmd
format MNI space coordinates

### Seed region of interest (ROI)
<!-- Regions of interest (definition and transformation into freesurfer long space) --> Seed regions were ... mm spheres in the precuneus (MNI: x,y,z = x,x,x) associated with the default mode network, and the Nucleus Accumbens (MNI: x,y,z = x,x,x) by averaging the time series across voxels.

@@

<!-- GM mask: Group*Time Interaction -->
Parametric and non-parametric significance test for the model testing for group-time-interaction did not show any different results when using a grey matter mask. Again, parametric estimation and non-parametric estimation differed in regard to the group-time-interaction of PCC and voxel ($18,42,30$) in the connectivity maps without GSR correction. While co-activation was significant in parametric estimation ($Z = 4.72$, $q_{FDRcorr} = 0.040$), it was non-significant when using wild bootstrap ($q_{FDRcorr} = 0.998$)<!-- also FWE-corr n.s -->.

>>>>

### Seed region of interest (ROI)
<!-- Regions of interest (definition and transformation into freesurfer long space) --> Seed regions were ... mm spheres in the precuneus ((MNI)X,Y,Z = x,x,x) associated with the default mode network, and the Nucleus Accumbens (x,x,x) by averaging the time series across voxels.

@@

<!-- GM mask: Group*Time Interaction -->
Parametric and non-parametric significance test for the model testing for group-time-interaction did not show any different results when using a grey matter mask. Again, parametric estimation and non-parametric estimation differed in regard to the group-time-interaction of PCC and voxel ($18,42,30$) in the connectivity maps without GSR correction. While co-activation was significant in parametric estimation ($Z = 4.72$, $q_{FDRcorr} = 0.040$), it was non-significant when using wild bootstrap ($q_{\mathrm{FDRcorr}} = 0.998$)<!-- also FWE-corr n.s -->.
